\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
copies paper from devnew
verslag

\subsubsection{Finding twins and false twins}
The algorithm \textit{gettwins} can be found in appendix \ref{gettwins}. In line 2-10 two lists, \textit{nbs} and \textit{nbs2}, are created. Both lists contains $n$ sorted sublists. In the former list each sublist contains all the neighbours of a node and in the latter each sublist contains all the neighbours of a node and also the node itself. Finding all the neighbours only require going though all the edges once, so the time complexity is $O(m)$. The sorting algorithm has time complexity $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$. \\\newline In line 11-16 a dictionary \textit{falsetwins} is created where the keys are all the items from \textit{nbs} and the values a list of the corresponding vertices. Since \textit{nbs} has length $n$ and \textit{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$. In line 23 the items in the \textit{falsetwins} with only one vertex as value are removed. This is $O(n)$, since len() has $O(1)$. The remaining values of the dictionary \textit{falsetwins} are now all the sets of false twins as defined in definition \ref{deffalsetwins}. A similar dictionary \textit{twins} is created where the keys are the items from \textit{nbs2}. The time complexity of \textit{gettwins} is thus $O(n^2 \log n)$.
%BRON https://wiki.python.org/moin/TimeComplexity

>>>>

\subsubsection{Finding twins and false twins}
The algorithm \textit{gettwins} can be found in appendix \ref{gettwins}. In line 2-10 two lists, \textit{nbs} and \textit{nbs2}, are created. Both lists contains $n$ sorted sublists. In the former list each sublist contains all the neighbours of a node and in the latter each sublist contains all the neighbours of a node and also the node itself. Finding all the neighbours only require going though all the edges once, so the time complexity is $O(m)$. The sorting algorithm has time complexity $O(n \log n)$, since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$. In most test instances the average length of the neighbours is however not even close to $n$, so this really is a worst case complexity.  \\\newline In line 11-16 a dictionary \textit{falsetwins} is created where the keys are all the items from \textit{nbs} and the values a list of the corresponding vertices. Since \textit{nbs} has length $n$ and \textit{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$. In line 23 the items in the \textit{falsetwins} with only one vertex as value are removed. This is $O(n)$, since len() has $O(1)$. The remaining values of the dictionary \textit{falsetwins} are now all the sets of false twins as defined in definition \ref{deffalsetwins}. A similar dictionary \textit{twins} is created where the keys are the items from \textit{nbs2}. The time complexity of \textit{gettwins} is thus $O(n^2 \log n)$.
%BRON https://wiki.python.org/moin/TimeComplexity
